Bare Demo of IEEEtran.cls for Journals

### 2019-12-10 2-oracle/report/paper.tex
experiment data update

% ljy
\subsection{Ensemble of Two Methods}
To improve the performance of the model, we add an ensemble network for CNN and template matching. It takes the output of CNN and template matching as input, and through a linear regression, produces the score of each class.

@@

\begin{table}[h]
	\centering
	\caption{Accuracy for Different Models}
	\label{tab:result}
	\begin{tabular}{|c|c|c|}
		\hline
		                            & Cat10  & Cat40  \\\hline
		DNN ($\delta=0.5$)          & 0.8475 & 0.5275 \\\hline
		DNN Ensemble ($\delta=0.5$) & 0.8000 & 0.56   \\\hline
		TM ($\Delta=150$, NMSE)     & 0.7775 & 0.6325 \\\hline
		TM ($\Delta=150$, NCCOR)    & 0.8000 & 0.6500 \\\hline
		TM Ensemble ($\Delta=?$)    & ?      & ?      \\\hline
	\end{tabular}
\end{table}

>>>>

% ljy
\subsection{Ensemble of Two Methods}
To improve the performance of the model, we add an ensemble network for CNN. (UNFINISHED)

@@

\begin{table}[h]
	\centering
	\caption{Accuracy for Different Models}
	\label{tab:result}
	\begin{tabular}{|c|c|c|}
		\hline
		                            & Cat10  & Cat40  \\\hline
		DNN ($\delta=0.5$)          & 0.8475 & 0.5275 \\\hline
		DNN Ensemble ($\delta=0.5$) & 0.8000 & 0.56   \\\hline
		TM ($\Delta=150$, NMSE)     & 0.7575 & 0.6125 \\\hline
		TM ($\Delta=150$, NCCOR)    & 0.8475 & 0.7000 \\\hline
		TM Ensemble ($\Delta=?$)    & ?      & ?      \\\hline
	\end{tabular}
\end{table}
